---
title: <span style="color:blue">Quick Top Ten Graph</span>
author: "Mike McLaughlin"
date: "March 5, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## <span style="color:blue">Quick Top Ten Graph - Time Savings</span>

This application will replace a processes that is currently completed using Microsoft Excel.  

- Each mornign a text file is automatically downloaded.

- Average file contains 95K lines of data.

- Data must be summarized and a table showing the top ten transactions by volume must be printed and made available to seneior managers.

- A graph is included at the request of one manager.

The process takes about 15 minutes to be completed by an experienced analyst.   However, staff turn-over can result in errors and delays.   This new process will take about 5 minutes and reduce errors.

## <span style="color:blue">Requirements</span>

- Text File with field names in the first row.
- File must contain numeric and text fields.
- Understanding of the data being processed - Otherwise, the graphs may not make sense.

The basic assumption is that a person creating these graphs understands the data and the purpose of the graph.   

## <span style="color:blue">Output Samples</span> 

This will generate a graph and a table.

####<span style="color:blue">Sample Graph and Table</span>
```{r graphs, echo=FALSE, warning=FALSE,fig.width=10,fig.height=4.5}
rm(list=ls())
library("ggplot2")
library("gridExtra")
library("plyr")

#-------------------------


sampleGraphFile2 <- read.delim("C:/2017/Blog/Data_Files/cntry_cnt.txt",header=TRUE,sep=",",comment.char = "")
df2 <- data.frame(sampleGraphFile2)


df2 <- sampleGraphFile2


dfSortPlot2 <- head(arrange(df2,desc(df2$Unique.Vistors)), n = 10)
dfSortPlot2 <- dfSortPlot2[,1:2]


Plot2 <- ggplot(dfSortPlot2, aes(x=dfSortPlot2[,1], y=dfSortPlot2[,2])) +
  geom_bar(stat='identity',fill="blue", colour="black") +
  xlab("Category") +  ylab("") +
  coord_flip() +
  scale_fill_hue() +
  theme_bw()

print("Graph - Tab 1")
Plot2

print("Table - Tab 2")
dfSortPlot2

```

table with code.



## <span style="color:blue">Next Steps</span>

- <span style="color:blue">Add additonal calculations such as averages, factors and standard diviations.</span>
- <span style="color:red">Review security concerns at this process resides on an external server.</span>
- <span style="color:blue">If security is a concern, review cost to build in-house system.</span>
- <span style="color:blue">Train additional staff on the process.</span>
</span>